Bow shocks, bow waves, and dust waves. III. Diagnostics

### 2019-03-30 papers/Papers1234/app-cloudy-dust-heating.tex
Fix abstract for Paper III
Finish source 342 revision - start on general intro

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sed-comparison}
  \caption{Comparison between the spectral energy distribution (SED)
    of a typical OB star (blue line) and the interstellar radiation
    field in the solar neighborhood (orange line).  The OB star is the
    \SI{20}{M_\odot} model from Table~\ref{tab:stars} and is plotted for a
    distance from the star of \SI{1}{pc}.  The interstellar SED is
    from \citet{Mathis:1983a} and is multiplied by \num{80} so that
    the total FUV-to-NIR flux is equal for the two SEDs.}
  \label{fig:sed-comparison}
\end{figure}

@@

\subsubsection{Stochastic single-photon heating}

When the radiation field is sufficiently dilute, then a grain that
absorbs a photon has sufficient time to radiate all that energy away
before it absorbs another photon \citep{Duley:1973a}.  In this case,
the emitted infrared spectrum for \(\lambda < \SI{50}{\um}\) becomes
relatively insensitive of the energy density of the incident radiation
\citep{Draine:2001a}.  However, this is most important for the very
smallest grains.  From equation~(47) of \citet{Draine:2001a}, one
finds that grains with sizes larger than
\(a = \SI{0.005}{\um} = \SI{5}{nm}\) (the smallest size included in
our Cloudy models) should be close to thermal equilibrium for
\(U > 30\), which is small compared with typical bow shock values
(\(U = \text{\numrange{e3}{e6}}\)).  As mentioned above, PAHs are not
expected to be present in the interior of \hii{} regions.
\citealp{Desert:1990a} found them to be strongly depleted for
\(U > 100\) around O stars.  However, other types of ultra-small
grains, down to sub-nm sizes \citep{Xie:2018a} may be present in bows,
and stochastic heating \emph{would} be important for grains with
\(a = \SI{1}{nm}\) if \(U < \num{e5}\).  Note, however that grains
smaller than \SI{0.6}{nm} would be destroyed by sublimation after
absorbing a single He-ionizing photon.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sed-comparison}
  \caption{Comparison between the spectral energy distribution (SED)
    of a typical OB star (blue line) and the interstellar radiation
    field in the solar neighborhood (orange line).  The OB star is the
    \SI{20}{M_\odot} model from Table~1 of Paper~I and is plotted for
    a distance from the star of \SI{1}{pc}.  The interstellar SED is
    from \citet{Mathis:1983a} and is multiplied by \num{80} so that
    the total FUV-to-NIR flux is equal for the two SEDs.}
  \label{fig:sed-comparison}
\end{figure}

@@

\subsubsection{Stochastic single-photon heating}
\label{sec:stoch-single-phot}
When the radiation field is sufficiently dilute, then a grain that
absorbs a photon has sufficient time to radiate all that energy away
before it absorbs another photon \citep{Duley:1973a}.  In this case,
the emitted infrared spectrum for \(\lambda < \SI{50}{\um}\) becomes
relatively insensitive of the energy density of the incident radiation
\citep{Draine:2001a}.  However, this is most important for the very
smallest grains.  From equation~(47) of \citet{Draine:2001a}, one
finds that grains with sizes larger than
\(a = \SI{0.005}{\um} = \SI{5}{nm}\) (the smallest size included in
our Cloudy models) should be close to thermal equilibrium for
\(U > 30\), which is small compared with typical bow shock values
(\(U = \text{\numrange{e3}{e6}}\)).  As mentioned above, PAHs are not
expected to be present in the interior of \hii{} regions.
\citealp{Desert:1990a} found them to be strongly depleted for
\(U > 100\) around O stars.  However, other types of ultra-small
grains, down to sub-nm sizes \citep{Xie:2018a} may be present in bows,
and stochastic heating \emph{would} be important for grains with
\(a = \SI{1}{nm}\) if \(U < \num{e5}\).  Note, however that grains
smaller than \SI{0.6}{nm} would be destroyed by sublimation after
absorbing a single He-ionizing photon.

### 2019-03-30 papers/Papers1234/bs-bw-dw-03.tex
Finish source 342 revision - start on general intro

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Stellar bow shocks, bow waves, and dust waves all result from the
  action of a star's wind and radiation pressure on a stream of dusty
  plasma that flows past it.  The dust in these bows emits prominently
  at mid-infrared wavelengths in the range \SIrange{8}{60}{\um}. We
  propose a novel diagnostic method, the \(\tau\)--\(\eta\) diagram,
  for analyzing these bows, which is based on comparing the fractions
  of stellar radiative energy and stellar radiative momentum that is
  trapped by the bow shell.  This diagram allows the discrimination of
  wind-supported bow shocks, radiation-supported bow waves, and dust
  waves in which grains decouple from the gas.  For the wind-supported
  bow shocks, it allows the stellar wind mass loss rate to be
  determined.  We critically compare our method with a previous method
  that has been proposed for determining wind mass-loss rates from bow
  shock observations. This comparison points to ways in which both
  methods can be improved and suggests a downward revision by a factor
  of two with respect to previously reported mass-loss rates.  From a
  sample of 23 mid-infrared bow-shaped sources, we identify 4 strong
  candidates for radiation-supported bow waves, which need to be
  confirmed by more detailed studies, but no strong candidates for
  dust waves.
\end{abstract}

@@

In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
presented a taxonomy of stellar bows, which we divided into
wind-supported bow shocks (WBS) and various classes of
radiation-supported bows.  When the dust and gas remains well-coupled
(Paper~I), these are optically thin radiation-supported bow waves
(RBW) and optically thick radiation-supported bow shocks (RBS).  When
the dust decouples from the gas (Paper~II), one has inertia-confined
dust waves (IDW) and drag-confined dust waves (DDW).

@@

The outline of the paper is as follows. In
\S~\ref{sec:energy-trapp-vers} we describe how the optical depth and
the gas pressure in the bow shell can be estimated from a small number
of observed quantities.  In \S~\ref{sec:eta-tau-diagnostic} we place
observed bow sources on a diagnostic diagram of these two quantities
and discuss the influence of observational errors and systematic model
uncertainties. In \S~\ref{sec:cand-radi-supp} we use the diagram to
identify some candidates for radiation-supported bows. In
\S~\ref{sec:grain-temp-emiss} we calculate the grain emissivity as a
function of the stellar radiation field around OB stars.  In
\S~\ref{sec:stellar-wind-mass} we compare two different methods of
estimating the stellar wind mass loss rates from observations of the
bows.  In \S~\ref{sec:conclusions} we summarise out findings.

>>>>

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Stellar bow shocks, bow waves, and dust waves all result from the
  action of a star's wind and radiation pressure on a stream of dusty
  plasma that flows past it.  The dust in these bows emits prominently
  at mid-infrared wavelengths in the range \SIrange{8}{60}{\um}. We
  propose a novel diagnostic method, the \(\tau\)--\(\eta\) diagram,
  for analyzing these bows, which is based on comparing the fractions
  of stellar radiative energy and stellar radiative momentum that is
  trapped by the bow shell.  This diagram allows the discrimination of
  wind-supported bow shocks, radiation-supported bow waves, and dust
  waves in which grains decouple from the gas.  For the wind-supported
  bow shocks, it allows the stellar wind mass-loss rate to be
  determined.  We critically compare our method with a previous method
  that has been proposed for determining wind mass-loss rates from bow
  shock observations. This comparison points to ways in which both
  methods can be improved and suggests a downward revision by a factor
  of two with respect to previously reported mass-loss rates.  From a
  sample of 23 mid-infrared bow-shaped sources, we identify at least 4
  strong candidates for radiation-supported bow waves, which need to
  be confirmed by more detailed studies, but no strong candidates for
  dust waves.
\end{abstract}

@@

Early searches for bow shocks around OB stars \citep{van-Buren:1995a}
concentrated on runaway stars \citep{Hoogerwerf:2011a} that have been ejected at high
velocities (\(> \SI{30}{km.s^{-1}}\)) due to multi-body encounters in
star clusters or the core-collapse supernova of a binary companion.

Walkaways \citep{Renzo:2018a}

Absence of bow shocks \citep{Huthoff:2002a} HMXRBs \citep{Prisegen:2019a}

High-mass x-ray binaries

WISE surveys \citep{Peri:2012a, Peri:2015a} and Spitzer surveys \citep{Kobulnicky:2016a, Kobulnicky:2017a, Kobulnicky:2018a}.  Particular high-mass star forming regions such as Carina \citep{Sexton:2015a}, Cygnus~X \citep{Kobulnicky:2010a}

Galactic Center region H1 \citep{Dong:2017a} (UCHII)

were originally searched for \citep{Noriega-Crespo:1997b} in the context of

In the Orion Nebula, at least three different classes of stellar bow
shocks have been identified. As well as small number of OB bow shocks \citep{Smith:2005a, ODell:2001c},

HMXRB in external galaxies, possible bowshock in LMC~X-1 \citep{Hyde:2017a}.

Non-thermal radio emission from BD+43~3654 \citep{Benaglia:2010a}, has been searched for but

Analytic and semi-analytic thin-shell models of bow shocks
\citep{van-Buren:1992a, Wilkin:1996a, Canto:1996a}, including
non-spherical winds and nonaxisymmetric bows \citep{Wilkin:2000a,
  Henney:2002a, Canto:2005a, Tarango-Yong:2018a}.  Numerical
hydrodynamic simulations \citep{Matsuda:1989a, Raga:1997a}

Slow subsonic velocities of a star through its \hii{} region may be
sufficient \citep{Mackey:2015a, Mackey:2016a} to distort the inner
stellar wind shock and produce a bow shock appearance, even though
there is no shock in the dusty ambient stream.

Cooler red supergiant and asymptotic giant branch stars
\citep{Ueta:2008a, Sahai:2010a, Cox:2012a}.

In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
presented a taxonomy of stellar bows, which we divided into
wind-supported bow shocks (WBS) and various classes of
radiation-supported bows.  When the dust and gas remains well-coupled
(Paper~I), these are optically thin radiation-supported bow waves
(RBW) and optically thick radiation-supported bow shocks (RBS).  When
the dust decouples from the gas (Paper~II), inertia-confined dust
waves (IDW) and drag-confined dust waves (DDW) can result.

@@

The outline of the paper is as follows. In
\S~\ref{sec:energy-trapp-vers} we describe how the optical depth and
the gas pressure in the bow shell can be estimated from a small number
of observed quantities.  In \S~\ref{sec:eta-tau-diagnostic} we place
observed bow sources on a diagnostic diagram of these two quantities
and discuss the influence of observational errors and systematic model
uncertainties. In \S~\ref{sec:cand-radi-supp} we use the diagram to
identify some candidates for radiation-supported bows. In
\S~\ref{sec:grain-temp-emiss} we calculate the grain emissivity as a
function of the stellar radiation field around OB stars.  In
\S~\ref{sec:stellar-wind-mass} we compare two different methods of
estimating the stellar wind mass loss rates from observations of the
bows. In \S~\ref{sec:discussion} we discuss various groups of bows
that require special treatment due to their diverse physical
conditions. In \S~\ref{sec:conclusions} we summarise out findings.

### 2019-03-30 papers/Papers1234/sec-observational-diagnostics.tex
Finish source 342 revision - start on general intro

In a series of papers \citeauthor{Kobulnicky:2018a} provide an
extensive mid-infrared-selected sample of over 700 candidate stellar
bow shock nebulae (\citealp{Kobulnicky:2016a, Kobulnicky:2017a,
  Kobulnicky:2018a}, hereafter K16, K17, and K18).  For 20 of these
sources, reliable distances and spectral classifications are provided
in Table~5 of K17 and Tables~1 and~2 of K18. In this section, we
outline how we obtain \(\tau\) and \(\eta\shell\) from the data in these
catalogs, while further aspects of the \citeauthor{Kobulnicky:2018a}
material are discussed in \S~\ref{app:bow-shock-data}.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
    identified in K18.  Red crosses show the emissivities given in
    K18's Table~2 as a function of the radiation field \(U\), while
    the solid gray line shows the emissivities that they claim to be
    using from \citet{Draine:2007a}.  The dashed line shows the
    emissivities that we believe they should have been using, which
    correct for the marked difference in spectral energy distribution
    between OB stars and the Galactic interstellar radiation field
    (see App.~\ref{sec:grain-temp-emiss}).}
  \label{fig:k18-emissivity}
\end{figure}

@@

In principle, both methods are valid and their different assumptions
and dependencies on observed quantities and auxiliary parameters
provide an important cross check on one another.  However, as
explained in detail in \S~\ref{sec:grain-temp-emiss}, the
\(j_\nu(U)\) relation depends on the shape of the illuminating SED,
which means that the \citet{Draine:2007a} models require modification
when applied to grains around OB stars.  In addition, when attempting
to replicate the K18 values of \(j_{70}\) we find that they only
follow the \citet{Draine:2007a} values for \(U > \num{e4}\), tending
to a constant value for weaker radiation fields.  The situation is
summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
directly from Table~2 of K18 are shown by red crosses, the values they
claim to be using are shown by the gray solid line (this curve is
consistent with that shown in K18 Fig.~2), and the values they
\textit{should} have been using are shown by the gray dashed line.

@@

We choose not make this correction to the \(\tau\)--\(\eta\shell\)
method in this paper since we want to test the methods using published
data alone and without excessive fine-tuning.  However, for future
applications an empirical measurement of the shell thicknesses would
clearly help improve the reliability of the method.

@@

Therefore, we have shown that a neutral shell is not consistent with
the observational data for source~342, and so this is unlikely to be
the explanation for the seemingly high mass loss rate.  Instead, it is
possible that the explanation is simply that the stellar luminosity
has been underestimated, since the luminosity class is not well
constrained by spectroscopy (K18).  If the star were B1~III instead of
B1~V, then the luminosity would be 4 times higher.  This could be due
to a combination of having underestimated the distance and having
underestimated the foreground extinction.  The assumed distance of
\(D= \SI{1.3}{kpc}\) comes from a study of eclipsing binaries in the
Cygnus~OB2 association \citep{Kiminki:2015a}, but GAIA~DR2 parallaxes
for the association clearly show two sub-groups at
\(D = \SI{1.76}{kpc}\) and \SI{1.35}{kpc}, with the farther group
being the dominant one \citep{Berlanas:2019a}.  The GAIA parallax for
source~342 yields a median and 90\% confidence interval of
\(1.65^{+0.18}_{-0.16} \, \si{kpc}\) (same methodology as
App.~\ref{sec:hd-53367-v750}),
% \SIrange{1.49}{1.83}{kpc}
which clearly indicates it is in the farther group.  Taking the median
distance of \SI{1.65}{kpc} would raise \(L_*\) by a factor 1.61 and
increasing the visual extinction \(A_V\) by 1 magnitude would give an
additional factor of 2.51 for a total increase by \(\approx 4\), as we
are looking for.  To find the effects on the derived quantities, we
can sum the Jacobian elements in the first two rows of
Table~\ref{tab:derived-parameters}, multiplied by the changes in
observed log quantities: \(\Delta D \approx \SI{+0.1}{dex}\) and
\(\Delta L_* \approx \SI{+0.6}{dex}\). For example:
\begin{equation}
  \label{eq:delta-derived}
  \Delta\tau = J_D(\tau)\, \Delta D + J_{L_*}(\tau)\, \Delta L_*
\end{equation}
and similarly for the other quantities.  This yields
\(\Delta \tau \approx \SI{-0.4}{dex}\),
\(\Delta \eta\shell \approx \SI{-0.9}{dex}\),
\(\Delta \dot{M} \approx \SI{-0.3}{dex}\), and
\(\Delta \dot{M}_{\text{K18}} \approx \SI{-0.1}{dex}\).  In
Figure~\ref{fig:mass-loss-vs-luminosity}a this would move source~342
substantially to the right and slightly down, thus transforming it
from an extreme outlier to an unremarkable source in the center of the
pack.  It would be disappointing if such a prosaic explanation were
the correct one, given all the other peculiarities of this source
listed in the first paragraph of this section.  However, based on
current evidence, the more interesting and exotic explanations are
less plausible.

% Using emissivity at different wavelength, such as \SI{24}{\um}.  No
% good reason to fear stochastic heating.  They mention not getting 70/24 ratio right.  Probably be better with our correction.

% How both the UV opacity and the IR emissivity depend on the same VSG grains.

>>>>

In a series of papers \citeauthor{Kobulnicky:2018a} provide an
extensive mid-infrared-selected sample of over 700 candidate stellar
bow shock nebulae (\citealp{Kobulnicky:2016a, Kobulnicky:2017a,
  Kobulnicky:2018a}, hereafter K16, K17, and K18).  For 20 of these
sources, reliable distances and spectral classifications are provided
in Table~5 of K17 and Tables~1 and~2 of K18. In this section, we
outline how we obtain \(\tau\) and \(\eta\shell\) from the data in
these catalogs, while further aspects of the
\citeauthor{Kobulnicky:2018a} material are discussed in
\S~\ref{app:bow-shock-data}.  As this paper was being written, we
became aware of a new mass-loss study that greatly expands on the
earlier results of K18 (H.~Kobulnicky, priv.~comm.).  The new study
includes 70 bow shock sources and incorporates Gaia distances and
proper motions, together with new optical/IR spectroscopy of the
central stars.  Apart from making use of an updated spectral
classification of one source (\S~\ref{sec:anomalous-b-star}), we have
elected to concentrate on only the published K18 sample in this paper,
but will address the expanded sample in future publications.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
    identified in K18.  Red crosses show the emissivities given in
    K18's Table~2 as a function of the radiation field \(U\), while
    the solid gray line shows the emissivities that they claim to be
    using from \citet{Draine:2007a}.  The dashed line shows the
    emissivities that we believe they should have been using, which
    correct for the marked difference in spectral energy distribution
    between OB stars and the Galactic interstellar radiation field
    (see \S~\ref{sec:grain-temp-emiss}).}
  \label{fig:k18-emissivity}
\end{figure}

@@

In principle, both methods are valid and their different assumptions
and dependencies on observed quantities and auxiliary parameters
provide an important cross check on one another.  However, as
explained in detail in \S~\ref{sec:grain-temp-emiss}, the \(j_\nu(U)\)
relation depends on the shape of the illuminating SED, which means
that the \citet{Draine:2007a} models require modification when applied
to grains around OB stars.  In addition, when attempting to replicate
the K18 values of \(j_{70}\) we find that they only follow the
\citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
constant value for weaker radiation fields.  The situation is
summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
directly from Table~2 of K18 are shown by red crosses, the values they
claim to be using are shown by the gray solid line (this curve is
consistent with that shown in K18 Fig.~2), and the values they
\textit{should} have been using are shown by the gray dashed
line. Note that this correction may also resolve the color temperature
discrepancy noted by \citet{Kobulnicky:2017a}.

@@

We choose not make this correction to the \(\tau\)--\(\eta\shell\)
method in this paper since we want to test the methods using published
data alone and without excessive fine-tuning.  However, for future
applications an empirical measurement of the shell thicknesses would
clearly help improve the reliability of the \(\tau\)--\(\eta\shell\)
method.

It is hard to say which of the two mass-loss methods is ``better'',
except that the \(\tau\)--\(\eta\shell\) method has the advantage of
being able to identify radiation-supported bows, for which the mass
loss cannot be determined.  We recommend that both be employed if
possible as a cross-check on one another.  The
\(\tau\)--\(\eta\shell\) method has the disadvantage of requiring
shell photometry at a range of wavelengths: \SIrange{8}{70}{\um} in
order to be sure of covering the bulk of the grain emission, whereas
the K18 method needs only the \SI{70}{\um} surface brightness.  On the
other hand, we suspect that this makes the \(\tau\)--\(\eta\shell\)
method less sensitive to possible variations in grain composition and
size distribution.  This is because it depends on the average grain
opacity over a broad range of ultraviolet wavelengths, rather than the
emissivity in a single infrared band.  Additionally, many bows are
weak emitters at \SI{70}{\um}, whereas the background emission from
the PDRs surrounding \hii{} regions is very bright and variable.  The
contrast of the bow against the background is usually much higher at
\SI{24}{\um}, but K18 avoid this waveband on the grounds that it may
be dominated by emission from stochastic heating of very small grains.
We maintain that this avoidance is over-conservative (see
\S~\ref{sec:stoch-single-phot}), since (i)~the high circumstellar
radiation fields (\(U > 1000\)) mean that stochastic heating is only
relevant for ultra-small nanometer-sized grains \citep{Draine:2001a},
and (ii)~the most important class of such grains in the general ISM is
PAHs, and these are destroyed by the ionizing radiation from O~stars
\citep{Desert:1990a}.  Although PAHs may survive in bows around
B~stars, which lack the energetic photons (\(h\nu > \SI{40}{eV}\))
that most efficiently destroy them \citep{Lebouteiller:2007a}, their
contribution to the \SI{24}{\um} emissivity is likely to be small
compared with the slightly larger grains (\(> \SI{5}{nm}\)), which are
in thermal equilibrium with the radiation field.  It may therefore be
worth modifying the K18 method to use the \SI{24}{\um} surface
brightness instead of \SI{70}{\um}.  In the case of the
\(\tau\)--\(\eta\shell\) method, this is all irrelevant since
equation~\eqref{eq:tau-empirical} is valid in a time-averaged sense,
irrespective of whether stochastic heating is important or not.

@@

Therefore, we have shown that source~342 cannot have a neutral shell
if we take the published observational data at face value.  However,
more recent spectroscopic observations revise the spectral
classification to B4~V (H.~Kobulnicky, priv.~comm.) and this would
change the picture completely.  A B4 dwarf, with effective temperature
of \SI{16700}{K} \citep[Tab.~4 of][]{Pecaut:2013a} would have a very
small ionizing luminosity. Interpolating on Table~4 of
\citet{Lanz:2007a}, we find \(S_{49} / L_4 \approx \num{4e-6}\), which
yields \(\tau\iftrap = 0.017\) from equation~\eqref{eq:tau-trap-rbw}.
At the same time, the revised spectroscopy implies a smaller \(L_*\)
by roughly a factor of 10, which increases the shell's derived
\(\tau\) by the same factor (eq.~[\ref{eq:tau-empirical}]), yielding
\(\tau \approx 0.05\).  Since we now have \(\tau > \tau\iftrap\) it is
possible that ionization front may be trapped, giving a predominately
neutral shell.  This also relies, however, on the radiation field from
the nearby Cygnus OB2 cluster being insufficient to ionize the shell.
Given that the cluster's stellar population \citep{Wright:2015a}
includes 3 WR stars and a handful of early-O supergiants, the ionizing
luminosity must be of order \SI{e51}{s^{-1}}.  In the absence of
absorption, and assuming that the true separation to be no more than a
few times larger than the projected separation, the cluster stars
would contribute over 100 times greater ionizing flux at the position
of source 34 than that due to the B4 star itself.  It is therefore
necessary for the source to lie outside of the cluster's \hii{} region
in order for the shell to be neutral.  It is quite plausible that this
might be the case, since radio continuum observations \citetext{Fig.~4
  of \citealp{Wendker:1991a} and Fig.~7 of \citealp{Tung:2017a}}
indicate that the neighborhood of source~342 is a local minimum in
free-free emission between discrete \hii{} regions of the Cygnus~X
complex, while Herschel maps \citep{Schneider:2016a} show the
presence of both warm and cold dust along the line of sight and clumps
of Class~0 and~I YSOs are seen nearby \citep{Beerer:2010a}, indicative
of shielded neutral/molecular gas.

%%%
%%% PREVIOUS VERSION, WHEN WE THOUGHT 342 WAS A B1V STAR
%%%
% % Therefore, we have shown that a neutral shell is not consistent with
% % the observational data for source~342, and so this is unlikely to be
% % the explanation for the seemingly high mass loss rate.  Instead, it is
% % possible that the explanation is simply that the stellar luminosity
% % has been underestimated, since the luminosity class is not well
% % constrained by spectroscopy (K18).  If the star were B1~III instead of
% % B1~V, then the luminosity would be 4 times higher.  This could be due
% % to a combination of having underestimated the distance and having
% % underestimated the foreground extinction.  The assumed distance of
% % \(D= \SI{1.3}{kpc}\) comes from a study of eclipsing binaries in the
% % Cygnus~OB2 association \citep{Kiminki:2015a}, but GAIA~DR2 parallaxes
% % for the association clearly show two sub-groups at
% % \(D = \SI{1.76}{kpc}\) and \SI{1.35}{kpc}, with the farther group
% % being the dominant one \citep{Berlanas:2019a}.  The GAIA parallax for
% % source~342 yields a median and 90\% confidence interval of
% % \(1.65^{+0.18}_{-0.16} \, \si{kpc}\) (same methodology as
% % App.~\ref{sec:hd-53367-v750}),
% % % \SIrange{1.49}{1.83}{kpc}
% % which clearly indicates it is in the farther group.  Taking the median
% % distance of \SI{1.65}{kpc} would raise \(L_*\) by a factor 1.61 and
% % increasing the visual extinction \(A_V\) by 1 magnitude would give an
% % additional factor of 2.51 for a total increase by \(\approx 4\), as we
% % are looking for.  To find the effects on the derived quantities, we
% % can sum the Jacobian elements in the first two rows of
% % Table~\ref{tab:derived-parameters}, multiplied by the changes in
% % observed log quantities: \(\Delta D \approx \SI{+0.1}{dex}\) and
% % \(\Delta L_* \approx \SI{+0.6}{dex}\). For example:
% % \begin{equation}
% %   \label{eq:delta-derived}
% %   \Delta\tau = J_D(\tau)\, \Delta D + J_{L_*}(\tau)\, \Delta L_*
% % \end{equation}
% % and similarly for the other quantities.  This yields
% % \(\Delta \tau \approx \SI{-0.4}{dex}\),
% % \(\Delta \eta\shell \approx \SI{-0.9}{dex}\),
% % \(\Delta \dot{M} \approx \SI{-0.3}{dex}\), and
% % \(\Delta \dot{M}_{\text{K18}} \approx \SI{-0.1}{dex}\).  In
% % Figure~\ref{fig:mass-loss-vs-luminosity}a this would move source~342
% % substantially to the right and slightly down, thus transforming it
% % from an extreme outlier to an unremarkable source in the center of the
% % pack.  It would be disappointing if such a prosaic explanation were
% % the correct one, given all the other peculiarities of this source
% % listed in the first paragraph of this section.  However, based on
% % current evidence, the more interesting and exotic explanations are
% % less plausible.
